---
title: "CancerRCDPredictor AI Synthesis Report"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M:%S')`"
output: 
  html_document:
    theme: flatly
params:
  logo: ""
  patient_id: ""
  cohort: ""
  shap_text: ""
  pharma_text: ""
  shap_payload: ""
  pharma_payload: ""
  chat_history: !r list()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

<style>
  h1.title { display: none !important; }
  body { font-size: 14px; font-family: 'Helvetica Neue', Helvetica, Arial, sans-serif; line-height: 1.6; color: #334155; }
  .section-title { color: #1e293b; border-bottom: 2px solid #cbd5e1; padding-bottom: 5px; margin-top: 30px; font-weight: bold; }
  .ai-text { background: #f8fafc; border: 1px solid #e2e8f0; padding: 15px; border-radius: 6px; white-space: pre-wrap; font-size: 14px; }
  .payload-text { background: #1e293b; color: #cbd5e1; padding: 15px; border-radius: 6px; white-space: pre-wrap; font-family: 'Courier New', Courier, monospace; font-size: 12px; overflow-x: auto; }
  .chat-user { background: rgba(96, 165, 250, 0.1); border-left: 4px solid #60a5fa; padding: 10px 15px; margin-bottom: 10px; border-radius: 0 6px 6px 0; }
  .chat-ai { background: rgba(139, 92, 246, 0.1); border-left: 4px solid #8b5cf6; padding: 10px 15px; margin-bottom: 10px; border-radius: 0 6px 6px 0; }
</style>

<table width="100%" style="border-bottom: 2px solid #e2e8f0; margin-bottom: 20px; padding-bottom: 10px;">
  <tr>
    <td valign="top" style="width: 80%; padding-right: 20px;">
      <h1 style="font-size: 22px; margin-top: 0; margin-bottom: 5px; color: #1e293b; line-height: 1.3;">
        CancerRCDPredictor AI Synthesis Report<br>
        <span style="font-size: 16px; color: #64748b;">(Precision Oncology Digital Tumor Board)</span>
      </h1>
      <p style="margin: 0; font-size: 15px;"><strong>Patient ID:</strong> `r params$patient_id` | <strong>Cohort:</strong> `r params$cohort`</p>
    </td>
    <td valign="top" align="right" style="width: 20%; padding-top: 3mm;">
      <img src="`r params$logo`" style="width: 85px; height: 85px; border-radius: 50%; box-shadow: 0 4px 20px rgba(255, 69, 0, 0.4); object-fit: cover; border: 2px solid rgba(255, 69, 0, 0.6); display: block; float: right;">
    </td>
  </tr>
</table>

<div style="background: #fef2f2; border-left: 4px solid #ef4444; padding: 12px; font-size: 13px; color: #991b1b; margin-bottom: 20px;">
  <strong>CAUTION:</strong> This clinical synthesis is AI-generated for academic research purposes and is NOT intended for clinical decision-making or patient care. The multi-omic signatures represent associative mathematical relationships, not proven causative biological pathways.
</div>

<h3 class="section-title">1. Clinical Synthesis &amp; Therapeutic Vulnerabilities</h3>
```{r section-shap, results='asis'}
cat('<div class="ai-text">\n')
cat(params$shap_text)
cat('\n</div>\n')
```

<h3 class="section-title">2. Pharmacogenomic Translation Matrix</h3>
```{r section-pharma, results='asis'}
cat('<div class="ai-text">\n')
cat(params$pharma_text)
cat('\n</div>\n')
```

<h3 class="section-title">3. Digital Tumor Board Inquiries</h3>
```{r render-chat, results='asis'}
if (length(params$chat_history) > 0) {
  for (msg in params$chat_history) {
    if (is.list(msg) && !is.null(msg$role) && !is.null(msg$content)) {
      if (msg$role == "user") {
        cat('<div class="chat-user"><strong>User:</strong><br>')
        cat(msg$content)
        cat('</div>\n')
      } else {
        clean_content <- gsub("<span.*?</span>", "", msg$content)
        cat('<div class="chat-ai"><strong>AI Assistant:</strong><br>')
        cat(clean_content)
        cat('</div>\n')
      }
    }
  }
} else {
  cat('<div style="color: #64748b; font-style: italic;">No inquiries were made during this session.</div>\n')
}
```

<h3 class="section-title">4. Audit Payloads (Raw Injections)</h3>
<p style="font-size: 13px; color: #64748b; margin-bottom: 10px;">The following raw text represents the exact contextual data payloads injected into the language model to generate the summaries above.</p>

#### SHAP Decoding Payload
```{r section-shap-payload, results='asis'}
cat('<div class="payload-text">\n')
cat(params$shap_payload)
cat('\n</div>\n')
```

<br>

#### Pharmacogenomic Translation Payload
```{r section-pharma-payload, results='asis'}
cat('<div class="payload-text">\n')
cat(params$pharma_payload)
cat('\n</div>\n')
```

<div style="font-size: 11px; color: #94a3b8; border-top: 1px solid #e2e8f0; padding-top: 10px; margin-top: 30px; text-align: center;">
Generated by CancerRCDPredictor Multi-Agent Framework. 
</div>
